### 2011-05-11 paper.tex
Added polynomial time reduction section

@@

\begin{theorem}\label{amplify}
Let $C$ be a \emph{$\{\Sigma,\Pi,\bp,\parity\}$}-constructible complexity class. Then \emph{$\bp \cdot C = \strongbp \cdot C$}.
\end{theorem}
Initially, this may seem to be obviously true for the same reasons that $\bp \cdot \p = \strongbp \cdot \bp$. The problem is that amplification requires running some machine which accepts a language in $C$ more than once. This requires the structure of $C$ to allow for such repetitions. This brings us to the concept of majority reductions.
\begin{definition}\label{defmajority}
We say that a complexity class $C$ is \emph{closed under majority reductions} if for any language $L$, the language $\majority(L) = \{(x_1,...,x_k) : k \in \mathbb{N}, |\{x_i : x_i \in L\}| \ge k/2\}$ is in $C$.
\end{definition}
Now, we see that majority reductions are exactly what we want for amplification:
\begin{lemma}\label{majorityimpliesamplify}
If $C$ is a complexity class which is closed under majority reductions, then\linebreak \emph{$\bp \cdot C = \strongbp \cdot C$.}
\end{lemma}
\begin{proof}
This is now the same application of the Chernoff bound which shows that $\bp \cdot \p = \strongbp \cdot \p$. Suppose $L$ is a language in $\bp \cdot C$. Then there is a language $M$ in $C$ such that $\pr_y [(x,y) \in M] > 2/3$ if $x\in L$ and $\pr_y [(x,y)\in M] < 1/3$ if $x\not\in L$, where the length of $y$ is polynomial in the length of $x$. Let $q$ be a polynomial, where $e^{-q(|x|)}$ is the desired error probability. Let $k = 48q(|x|)$.

Here is how we determine if a string $x$ is in $L$ with error probability $e^{-q(|x|)}$. Choose $k$ strings $y_1,y_2,...,y_k$ randomly. Then accept if a majority of $(x,y_1),(x,y_2),...,(x,y_k)$ are in $M$, which is possible to do since $\majority(M) \in C$. Let $X_i$ be an indicator variable which is $1$ if $(x,y_i)$ is in $M$. Then by the Chernoff bound,
\begin{align*}
\pr\left[\sum X_i < k/2\right] &= \pr\left[\sum X_i < (1 - 1/4)(2k/3)\right]\\
&< e^{-(1/4)^2 (2k/3) / 2}\\
&= e^{-q(|x|)} \\
&< 2^{-q(|x|)}
\end{align*}
We can do this for any polynomial $q$, so $L \in \strongbp \cdot C$. Hence, $\bp \cdot C = \strongbp \cdot C$.
\end{proof}

>>>>

\section{Polynomial Time Reductions}

One of the technical details that will arise in many of our results is the need for polynomial time reductions. In this section, we will establish that all $\{\Sigma,\Pi,\bp,\parity\}$-constructible complexity classes are closed under polynomial time reductions. In particular, we need.

\begin{prop}
Let $C$ be a $\{\Sigma,\Pi,\bp,\parity\}$-constructible complexity class and let $T$ be a mapping $\{0,1\}^n \to \{0,1\}^m$ defined by a polynomial time Turing machine. Then if $f \circ T \in C$, $f \in C$.
\end{prop}

This follows from the following four lemmas:

\begin{lemma}
If $C$ is a complexity class closed under polynomial time reductions. Then $\Sigma \cdot C$ is closed under polynomial time reductions.
\end{lemma}
\begin{proof}
We wish to show that if $f\circ T \in \Sigma \cdot C$, then $f \in \Sigma \cdot C$. Let $g$ be the partial function in $C$ such that if $f(T(x)) = 1$, then there exists $y\in\{0,1\}^{p(|T(x)|)} = \{0,1\}^{p'(|x|)}$ such that $g(\langle T(x),y\rangle) = 1$ and if $f(T(x)) = 0$, then for all $y$ $g(\langle T(x),y\rangle) = 0$. There exists a polynomial time Turing machine $T'$ that takes $\langle x, y\rangle$ to $\langle T(x), y\rangle$, so the function $h(\langle x, y\rangle) = g(\langle T(x), y\rangle)$ is in $C$.

Note that if $f(x) = 1$, then $f(T(x)) = 1$, so there exists $y$ such that $h(\langle x, y\rangle) = g(\langle T(x),y\rangle) = 1$, and if $f(x) = 0$, then for all $y$, $h(\langle x, y\rangle) = g(\langle T(x),y\rangle) = 0$, so since $h \in C$, $f \in \Sigma \cdot C$.
\end{proof}

\begin{lemma}
If $C$ is a complexity class closed under polynomial time reductions. Then $\Pi \cdot C$ is closed under polynomial time reductions.
\end{lemma}
\begin{proof}

\end{proof}

\begin{lemma}
If $C$ is a complexity class closed under polynomial time reductions. Then $\bp \cdot C$ is closed under polynomial time reductions.
\end{lemma}
\begin{proof}

\end{proof}

\begin{lemma}
If $C$ is a complexity class closed under polynomial time reductions. Then $\parity \cdot C$ is closed under polynomial time reductions.
\end{lemma}
\begin{proof}

\end{proof}

@@

\begin{theorem}\label{amplify}
Let $C$ be a \emph{$\{\Sigma,\Pi,\bp,\parity\}$}-constructible complexity class. Then \emph{$\bp \cdot C = \strongbp \cdot C$}.
\end{theorem}
Initially, this may seem to be obviously true for the same reasons that $\bp \cdot \p = \strongbp \cdot \bp$. The problem is that amplification requires running some machine which accepts a language in $C$ more than once. This requires the structure of $C$ to allow for such repetitions. This brings us to the concept of majority reductions.
\begin{definition}\label{defmajority}
We say that a complexity class $C$ is \emph{closed under majority reductions} if for any partial function $f \in C$, the partial function $\majority(f)$ defined by
$$\majority(f)(\langle x_1, \ldots, x_k\rangle) = 
\begin{cases}1 & \text{ if the number of $i$ such that }f(x_i) = 1\text{ is at least $\frac{k}{2}$} \\
0 & \text{ if the number of $i$ such that }f(x_i) = 0\text{ is at least $\frac{k}{2}$}\\
\x & \text{ otherwise}
\end{cases}$$
is in $C$.
\end{definition}
Now, we see that majority reductions are exactly what we want for amplification:
\begin{lemma}\label{majorityimpliesamplify}
If $C$ is a complexity class which is closed under majority reductions and polynomial time reductions, then\linebreak \emph{$\bp \cdot C = \strongbp \cdot C$.}
\end{lemma}
\begin{proof}
This is now the same application of the Chernoff bound which shows that $\bp \cdot \p = \strongbp \cdot \p$. Suppose $f$ is a partial function in $\bp \cdot C$. Then there is a partial function $g$ in $C$ such that $\pr_y [g(\langle x,y\rangle) = 1] > 2/3$ if $x\in L$ and $\pr_y [g(\langle x, y\rangle) = 0] > 2/3$ if $x\not\in L$, where the length of $y$ is equal to $p(|x|)$ for some polynomial $p$. Let $q$ be a polynomial, where $e^{-q(|x|)}$ is the desired error probability. Let $k = 48q(|x|)$.

Here is how we determine the value $f(x)$ with error probability $e^{-q(|x|)}$. Choose $k$ strings $y_1,y_2,...,y_k$ randomly, then return $h(\langle x, y_1y_2\cdots y_k\rangle) = \majority(g)(\langle \langle x, y_1 \rangle, \langle x, y_2 \rangle, \ldots, \langle x, y_k \rangle \rangle)$. Notice that $h$ can be easily reduced to $\majority(g)$ in polynomial time, and is therefore in $C$.
Let $X_i$ be an indicator variable which is $1$ if $g(\langle x,y_i\rangle)$ agrees with $f(x)$. We have that the $X_i$ are independent Bernoulli random variables with $\pr\left[X_i = 1\right] > \frac{2}{3}$.  Then by the Chernoff bound,
\begin{align*}
\pr\left[\sum X_i < k/2\right] &= \pr\left[\sum X_i < (1 - 1/4)(2k/3)\right]\\
&< e^{-(1/4)^2 (2k/3) / 2}\\
&= e^{-q(|x|)} \\
&< 2^{-q(|x|)}
\end{align*}
We can do this for any polynomial $q$, so $f \in \strongbp \cdot C$. Hence, $\bp \cdot C = \strongbp \cdot C$. Note that if $f(x) = \x$ then we have no restrictions on what we return.
\end{proof}
